### 2019-09-05 paper/1_introduction.tex
Delete conversion from complex to real DS

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,

\Disp {
\NC N_p \gg N_m \NR
}

In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

In this section, consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}} and \m {\V{\Phi} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
Set \m {\MC {T} \RB {N_p} =\CB {0, \dots, N_p-1}} for short.
For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
\Disp{
\NC \V {x}  \DB {\MC {A}}
=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR[+]
\NC \M {\Phi}  \DB {\MC {A}}
=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR[+]
}
That is, respectfully, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.

@@

\Result
{Definition: Restricted Isometry Property}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
}
}
That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.

@@

\Result
{Algorithm: Orthogonal Matching Pursuit}
{
\startitemize[n]
\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}, \m {\eta >0}.
\item Initialize
\Disp{
\NC \V{r}
\LA \NC \V{y} \NR[+]
\NC S
\LA \NC \varnothing \NR[+]
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
\Disp{
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR[+]
}
and insert \m {S \LA S \cup {i}}.
\item Compute
\Disp{
\NC \M{\Phi} ^\ddagger
\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \M{\Phi} \DB {S} ^\Adj \NR[+]
\NC \V{r}
\LA \NC \V{y} -\M{\Phi} \DB {S} ^\Adj \M{\Phi} ^\ddagger \V{y} \NR[+]
}
\item Break if
\Disp{
\NC \VNm {\V{r}} _2
<\NC \eta \NR[+]
}
where \m {\VNm {\M{\Phi} ^\ddagger} _1} denotes the operator norm.
\item Output 
\Disp {
\NC \Hat {\V {g}}
\LA \NC \M{\Phi} ^\ddagger \V{y} \NR[+]
}
\stopitemize
}
Here \m {\V{r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).

@@

\Result
{Definition.}
{
Define \m {\Rm {vec} \SB {\M {A}} \in \MB {V}_{\MB {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}}.
Formally,
\Disp{
\NC \RB {\Rm{vec} \SB {\M{A}}} \DB {m_1}
=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR[+]
}
The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
\Disp {
\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
=\NC x \NR[+]
}
}

\Result
{Definition.}
{
For \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}} and \m {\M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \MB {M}_{\MB {K}} \SB {N_1 N_3, N_2 N_4}} by
\Disp{
\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR[+]
}
}

@@

\Disp{
\NC \NC \RB {\Rm{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
\NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
}

@@

\Disp{
\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
\NC = \NC
\sum _{m_2 =0} ^{N_2 N_3 -1}
\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
\NC \NC \SixQ
\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
\NR[+]
}

>>>>

To motivate the need, we observe that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
\Disp {
\NC N_p \gg N_m \NR
}
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

In this section, consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}} and \m {\V{\Phi} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
Set \m {\MC {T} \RB {N_p} =\CB {0, \dots, N_p-1}} for short.
For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
\Disp {
\NC \V {x}  \DB {\MC {A}}
=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
\NC \M {\Phi}  \DB {\MC {A}}
=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR
}
That is, respectfully, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.

@@

\Result
{Definition: Restricted Isometry Property}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
}
}
That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.

@@

\Result
{Algorithm: Orthogonal Matching Pursuit}
{
\startitemize[n]
\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}, \m {\eta >0}.
\item Initialize
\Disp {
\NC \V{r}
\LA \NC \V{y} \NR
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
\Disp {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR
}
and insert \m {S \LA S \cup {i}}.
\item Compute
\Disp {
\NC \M{\Phi} ^\ddagger
\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \M{\Phi} \DB {S} ^\Adj \NR
\NC \V{r}
\LA \NC \V{y} -\M{\Phi} \DB {S} ^\Adj \M{\Phi} ^\ddagger \V{y} \NR
}
\item Break if
\Disp {
\NC \VNm {\V{r}} _2
<\NC \eta \NR
}
where \m {\VNm {\M{\Phi} ^\ddagger} _1} denotes the operator norm.
\item Output 
\Disp {
\NC \Hat {\V {g}}
\LA \NC \M{\Phi} ^\ddagger \V{y} \NR
}
\stopitemize
}
Here \m {\V{r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).

@@

\Result
{Definition.}
{
Define \m {\Rm {vec} \SB {\M {A}} \in \MB {V}_{\MB {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}}.
Formally,
\Disp {
\NC \RB {\Rm{vec} \SB {\M{A}}} \DB {m_1}
=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
}
The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
\Disp {
\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
=\NC x \NR
}
}

\Result
{Definition.}
{
For \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}} and \m {\M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \MB {M}_{\MB {K}} \SB {N_1 N_3, N_2 N_4}} by
\Disp {
\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR
}
}

@@

\Disp {
\NC \NC \RB {\Rm{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
\NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR
}

@@

\Disp {
\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
\NC = \NC
\sum _{m_2 =0} ^{N_2 N_3 -1}
\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
\NC \NC \SixQ
\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
\NR
}

### 2019-09-05 paper/2_problem_setting.tex
Delete conversion from complex to real DS

quad\startchapter [title={Problem Setting}]

@@

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR[+]
}
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
\Disp {
\NC \f_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
\NC \th_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
}
to get a simpler form
\Disp {
\NC \M{H}
\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
\NC \M{H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
}

@@

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \m {F_B} and analog precoder \m {F_R}.
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {W_B} and analog combiner \m {W_R}.
To set up notation, we list them as below.
\Disp {
\NC \M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y} \NR
\NC \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R} \NR
\NC \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H} \NR
\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR
}
Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
\Disp {
\NC \Nm {\M {F}_R \DB {n_H, n_R}}
= \NC 1, \NR[+]
\NC \Nm {\M {W}_R \DB {n_R, n_H}}
= \NC 1, \NR[+]
\NC n_H
= \NC 0, \dots N_H-1, \NR
\NC n_R
= \NC 0, \dots N_R-1 \NR
}
And we assume
\Disp {
\NC N_H \gg \NC N_R \NR[+]
\NC N_R \gg \NC N_Y \NR[+]
}

@@

We consider zero-mean, unity-variance additive white Gaussian noise (AWGN).
Since we restrict our discussion to a specific slice of time, this random process may be simply taken to be a matrix \m {\M{Z}} with each entry being i.i.d.\ standard Gaussian.
\Disp{
\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR[+]
}
We may introduce the effective channel
\Disp {
\NC \M{Y}
:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
}
We restate the equation with event space index for greater clarity,
\Disp {
\NC \NC \M{Y} \SB {\o_t, \o_h, \o_z, \o_r} \NR
\NC := \NC \M{W}_B \SB {\o_r} \M{W}_R \SB {\o_r} \RB {\M{H} \SB {\o_h} \M{F}_R \SB {\o_t} \M{F}_B \SB {\o_t} +\M{Z} \SB {\o_z} } \NR
}

@@

First, for short we set
\Disp {
\NC N_h
= \NC N_H^2 \NR[+]
\NC N_y
= \NC N_Y^2 \NR[+]
}
If we had followed the widely accepted approach of compressive channel sensing, we would have written
\Disp {
\NC \V {h}
\in \NC \MB {V}_{\MB {C}} \SB {N_h} \NR
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}} \NR[+]
\NC \V {y}
\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}} \NR[+]
\NC \V {z}
\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
\NC \V {z}
:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
\NC \M {Q}
\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
\NC \M {Q}
:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
}
to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M{H}}} to be
\Disp {
\NC \V {y}
=\M {Q} \V {h} +\V {z} \NR
}
As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
However, there is no guarantee, though, that \m {\V {h}} will be sparse.

@@

Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
\Disp {
\NC \M {K} \in  \NC \MB {M}_{\MB {C}} \SB {N_H, N_H} \NR
\NC \M {K} \DB {n_1, n_2}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
Roman \m{\Ss{e}} and \m{\Ss{i}} denote the natural base and imaginary unit, respectively.
Here recall that we have
\Disp{
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR[+]
}
Observe that, if we write
\Disp {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR[+]
}
which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
\Disp {
\NC \M {Y}
\in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
\NC \M {Y}
=\NC \M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
+\M {W}_B \M {W}_R \M {Z} \NR[+]
}
If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.

That is to say, a similar Kronecker product may be used.
To simplify notation, set
\Disp {
\NC \M {P}
\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
\NC \M {P}
:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR[+]
}
And accordingly
\Disp {
\NC \V {g}
\in \NC \MB {M}_{\MB {C}} \SB {N_h} \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}} \NR[+]
}
Then
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR[+]
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}}, \m{\g \geq 0}.
\item Calculate
\Disp {
\NC \Hat {\V {g}}
\LA \NC \startcases
\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
\stopcases \NR
}
\item Convert \m {\Hat {\V {g}}} back to the space domain, namely
\Disp {
\NC \Hat {G}
\LA \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Recover the estimated \m {\Hat {\M {H}}}, as
\Disp {
\NC \Hat {\M {H}}
\LA \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

>>>>

\startchapter [title={Problem Setting}]

@@

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
}
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
\Disp {
\NC \f_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR
\NC \th_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR
}
to get a simpler form
\Disp {
\NC \M{H}
\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
\NC \M{H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
}

@@

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \m {F_B} and analog precoder \m {F_R}.
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {W_B} and analog combiner \m {W_R}.
To set up notation, we list them as below.
\Disp {
\NC \M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y} \NR
\NC \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R} \NR
\NC \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H} \NR
\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR
}
Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
\Disp {
\NC \Nm {\M {F}_R \DB {n_H, n_R}}
= \NC 1, \NR
\NC \Nm {\M {W}_R \DB {n_R, n_H}}
= \NC 1, \NR
\NC n_H
= \NC 0, \dots N_H-1, \NR
\NC n_R
= \NC 0, \dots N_R-1 \NR
}
And we assume
\Disp {
\NC N_H \gg \NC N_R \NR
\NC N_R \gg \NC N_Y \NR
}

@@

We consider zero-mean, unity-variance additive white Gaussian noise (AWGN).
Since we restrict our discussion to a specific slice of time, this random process may be simply taken to be a matrix \m {\M{Z}} with each entry being i.i.d.\ standard Gaussian.
\Disp {
\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
}
We may introduce the effective channel
\Disp {
\NC \M{Y}
:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
}
We restate the equation with event space index for greater clarity,
\Disp {
\NC \NC \M{Y} \SB {\o_t, \o_h, \o_z, \o_r} \NR
\NC := \NC \M{W}_B \SB {\o_r} \M{W}_R \SB {\o_r} \RB {\M{H} \SB {\o_h} \M{F}_R \SB {\o_t} \M{F}_B \SB {\o_t} +\M{Z} \SB {\o_z} } \NR
}

@@

First, for short we set
\Disp {
\NC N_h
= \NC N_H^2 \NR
\NC N_y
= \NC N_Y^2 \NR
}
If we had followed the widely accepted approach of compressive channel sensing, we would have written
\Disp {
\NC \V {h}
\in \NC \MB {V}_{\MB {C}} \SB {N_h} \NR
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}} \NR
\NC \V {y}
\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}} \NR
\NC \V {z}
\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
\NC \V {z}
:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR
\NC \M {Q}
\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
\NC \M {Q}
:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
}
to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M{H}}} to be
\Disp {
\NC \V {y}
=\M {Q} \V {h} +\V {z} \NR
}
As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
However, there is no guarantee, though, that \m {\V {h}} will be sparse.

@@

Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
\Disp {
\NC \M {K} \in  \NC \MB {M}_{\MB {C}} \SB {N_H, N_H} \NR
\NC \M {K} \DB {n_1, n_2}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
Roman \m{\Ss{e}} and \m{\Ss{i}} denote the natural base and imaginary unit, respectively.
Here recall that we have
\Disp {
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR
}
Observe that, if we write
\Disp {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR
}
which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
\Disp {
\NC \M {Y}
\in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
\NC \M {Y}
=\NC \M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
+\M {W}_B \M {W}_R \M {Z} \NR
}
If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.

That is to say, a similar Kronecker product may be used.
To simplify notation, set
\Disp {
\NC \M {P}
\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
\NC \M {P}
:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR
}
And accordingly
\Disp {
\NC \V {g}
\in \NC \MB {M}_{\MB {C}} \SB {N_h} \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}} \NR
}
Then
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Let \m{\g \geq 0} be given.
\item Input \m {\M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y}, \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R}, \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H}, \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R}}, \m {\M {Y} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y}},
\item Find \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}} as in above.
\item Calculate
\Disp {
\NC \Hat {\V {g}}
\LA \NC \startcases
\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
\stopcases \NR
}
\item Convert \m {\Hat {\V {g}}} back to the space domain, namely
\Disp {
\NC \Hat {G}
\LA \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Recover the estimated \m {\Hat {\M {H}}}, as
\Disp {
\NC \Hat {\M {H}}
\LA \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}
